Verifying Demonstrations

### 2018-11-30 paper/analysis-performance.tex
Replaces \paragraph with \subsubsection where necessary
comments out our DB in performance, threshold computations in ledger subsection

\section{Performance and implementation}
\label{PerformanceAnalysis}
\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}

@@

\subsection{Distance-bounding anonymous credentials}
The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode. 
The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).

With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. 
The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
However, this can be reduced to four random number generations and one exponentiation using precomputation.

@@

If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
While this already takes longer than counting votes in national elections, the threshold is still very low. 
Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
In addition to the ledger computation, we need to consider the creation of the proof shares. \sonja{added the previous sentence to explain why anonpass shows up here. Shouldn't that be in the performance section? }
%Seb: I agree maybe we should move it to the previous subsection
According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
This yields \(
  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
  \SI{48}{\second}.
\) of processing. 
For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
Considering that online forums can facilitate mass coordination, the threshold approach seems not only inefficient but also potentially ineffective for verifiability.

>>>>

\section{Performance}
\label{PerformanceAnalysis}
\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}

@@

\subsection{Distance-bounding anonymous credentials}
The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode. 
The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).

% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. 
% The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
% Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
% However, this can be reduced to four random number generations and one exponentiation using precomputation.

@@

If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
While this already takes longer than counting votes in national elections, the threshold is still very low. 
% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
% In addition to the ledger computation, we need to consider the creation of the proof shares. \sonja{added the previous sentence to explain why anonpass shows up here. Shouldn't that be in the performance section? }
% %Seb: I agree maybe we should move it to the previous subsection
% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
% This yields \(
%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
%   \SI{48}{\second}.
% \) of processing. 
For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
